---
title: "SFN_2022"
author: "Roy Seo"
date: '2022-06-05'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('corrplot')
library('dplyr')
library('forcats')
library('ggbeeswarm')
library('ggplot2')
library('Hmisc')
library('lme4')
library('lmerTest')
library('magrittr')
library('plyr')
library('Rmisc')
library('tableone')
library('tidyverse')
library('knitr')

```

__grabbing the Variables of Interest

```{r}
redcap <- read.csv(file ='RepositorySubjectsPH-CP5192022_DATA_2022-05-19_1329 (1).csv')
df_redcap <- select(redcap, 
                    record_id, 
                    patientlist_gender_v2_v2, 
                    patientlist_ethnicgroup_v2_v2, 
                    syndrome_v2_v2, 
                    mocascore_9_v2_v2, 
                    mocascore_v2_v2, 
                    eti_v2_v2,
                    l_temporal_ct, 
                    r_temporal_ct, 
                    l_frontal_ct,
                    r_frontal_ct,
                    l_occipital_ct,
                    r_occipital_ct,
                    l_parietal_ct,
                    r_parietal_ct,
                    y7n1_visual_ct,
                    y7n2_somatomotor_ct,
                    y7n3_dorsalattn_ct,
                    y7n4_ventralattn_ct,
                    y7n5_limbic_ct,
                    y7n6_frontoparietal_ct,
                    y7n7_defaultmode_ct)

mbwc <- read.csv(file ='MBWC_database_SFN.csv')
df_mbwc <- select(mbwc, 
                  record_id, 
                  Age, 
                  Edu, 
                  TOPF_raw,
                  TOPF_Actual_SS, 
                  TOPF_Pred_SS,
                  WTAR_raw,
                  WTAR_SS,
                  eFSIQ, 
                  FAS_total_raw, 
                  FAS_total_T, 
                  Animals_raw, 
                  Animals_T, 
                  BNT_totalwstim_raw, 
                  BNT_totalwstim_T)


```

___merge

```{r}

# merge two data frames by ID
total  <- merge(df_redcap, df_mbwc, by="record_id")

sub_id <-c()
for (i in length(total$record_id)) {
  sub_id[i]<-ifelse(i<10, paste0("ID-0",i), paste0("ID-",i))}

 gender <-total$patientlist_gender_v2_v2
 ethnicity <-total$patientlist_ethnicgroup_v2_v2
 diagonoses <- total$syndrome_v2_v2
 moca_total <-total$mocascore_v2_v2 
 moca_lang <-total$mocascore_9_v2_v2
 etiology <- total$eti_v2_v2
 l_temporal <-total$l_temporal_ct
 r_temporal <-total$r_temporal_ct 
 l_frontal <- total$l_frontal_ct
 r_frontal <- total$r_frontal_ct
 l_occipital <- total$l_occipital_ct
 r_occipital <- total$r_occipital_ct
 l_parietal <-total$l_parietal_ct
 r_parietal <- total$r_parietal_ct
 y1_visual <- total$y7n1_visual_ct
 y2_somatomotor <- total$y7n2_somatomotor_ct
 y3_dorsalattn <- total$y7n3_dorsalattn_ct
 y4_ventralattn <-total$y7n4_ventralattn_ct
 y5_limbic <- total$y7n5_limbic_ct
 y6_frontoparietal <-total$y7n6_frontoparietal_ct
 y7_defaultmode <-total$y7n7_defaultmode_ct
 age <- total$Age
 edu <- total$Edu 
 topf_raw <-total$TOPF_raw
 topf_actual_ss <- total$TOPF_Actual_SS
 topf_pred_ss <- total$TOPF_Pred_SS
 wtar_raw <- total$WTAR_raw
 wtar_ss <- total$WTAR_SS
 wtar_efsiq <-total$eFSIQ
 fas_raw <-total$FAS_total_raw
 fas_t<- total$FAS_total_T
 animal_raw <- total$Animals_raw
 animal_t <- total$Animals_T
 bnt_raw <- total$BNT_totalwstim_raw
 bnt_t <-total$BNT_totalwstim_T
 



df <- data.frame(sub_id, 
                 gender,
                 age,
                 ethnicity,
                 edu, 
                 diagonoses,
                 etiology,
                 moca_total,
                 moca_lang, 
                 topf_raw,
                 topf_actual_ss,
                 topf_pred_ss, 
                 wtar_raw,
                 wtar_ss,
                 wtar_efsiq,
                 fas_raw,
                 fas_t,
                 animal_raw,
                 animal_t,
                 bnt_raw,
                 bnt_t,
                 l_frontal,
                 r_frontal, 
                 l_temporal, 
                 r_temporal, 
                 l_parietal,
                 r_parietal, 
                 r_occipital,
                 l_occipital,
                 y1_visual,
                 y2_somatomotor,
                 y3_dorsalattn,
                 y4_ventralattn,
                 y5_limbic,
                 y6_frontoparietal,
                 y7_defaultmode)


summary(total)
HC <- total$syndrome_v2_v2 == '3'
MCI <- total$syndrome_v2_v2 == '1'
Dementia <- total$syndrome_v2_v2 == '2'
summary(HC)

```


___factors

```{r}

sub_id <- as.factor(df$sub_id)
diag <- factor(df$diagonoses, levels = c("1", "2", "3", "4"))
eth <- factor(df$ethnicity, levels = c("Declined to Answer","Hispanic","Hispanic or Latino", "Not Hispanic or Latino","Not-Hispanic","Unavailable or Unknown"))
eti <- factor(df$etiology, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"))

#syndrome_v2_v2
##1-MCI
##2-Dementia
##3-Subjective Memory Complaint/Normal Cognition
##4-Unknown-Defer to Record

#eti_v2_v2
##0-
##1-Alzheimer's disease
##2-Lewy Body
##3-Parkinson's disease
##4-FTLD
##5-Vascular
##6-Mixed pathology
##7-Non-neurodegenerative
##8-Unknown
##9-Other
##10-


```

```{r}

#plot the outliers
boxplot(total$TOPF_Actual_SS,
  ylab = "topf_actual_SS",
  main = "Boxplot of topf_actual_SS")

boxplot(total$eFSIQ,
  ylab = "WTAR_eFSIQ",
  main = "Boxplot of WTAR_eFSIQ")

topf_actual_ss_outrm <- total$TOPF_Actual_SS [!total$TOPF_Actual_SS %in% boxplot.stats(total$TOPF_Actual_SS)$out]
boxplot(topf_actual_ss_outrm,
  ylab = "topf_actual_SS",
  main = "Boxplot of topf_actual_SS")

wtar_efsiq_outrm <- wtar_efsiq[!wtar_efsiq %in% boxplot.stats(wtar_efsiq)$out]
boxplot(wtar_efsiq_outrm,
  ylab = "wtar_efsiq_outrm",
  main = "Boxplot of wtar_efsiq_outrm")

```

```{r}
#find the quantiles (25th, 50th, and 75th percentiles) of the vector
quantile(df$topf_actual_ss, probs = c(.25, .5, .75), na.rm = TRUE)
quantile(df$wtar_efsiq, probs = c(.25, .5, .75), na.rm = TRUE)

```

___topf_ss < = 25% - Dementia:AD

```{r}
topf_bottom_y1visual <- lm(y1_visual ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss <= 95.25)) 
summary(topf_bottom_y1visual)

topf_bottom_y2somato <- lm(y2_somatomotor ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss <= 95.25)) 
summary(topf_bottom_y2somato)

topf_bottom_y3dorsalattn <- lm(y3_dorsalattn ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss <= 95.25)) 
summary(topf_bottom_y3dorsalattn)

topf_bottom_y4ventral  <- lm(y4_ventralattn ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss <= 95.25)) 
summary(topf_bottom_y4ventral )

topf_bottom_y5limbic <- lm(y5_limbic ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss <= 95.25)) 
summary(topf_bottom_y5limbic)

topf_bottom_y6frontoparietal <- lm(y6_frontoparietal ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss <= 95.25)) 
summary(topf_bottom_y6frontoparietal)

topf_bottom_y7defaultmode <- lm(y7_defaultmode ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss <= 95.25))
summary(topf_bottom_y7defaultmode)
```


```{r}
topf_top_y1visual <- lm(y1_visual ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss >= 114.50)) 
summary(topf_top_y1visual)

topf_top_y2somato <- lm(y2_somatomotor ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss >= 114.50))  
summary(topf_top_y2somato )

topf_top_y3dorsalattn <- lm(y3_dorsalattn ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss >= 114.50)) 
summary(topf_top_y3dorsalattn)

topf_top_y4ventral <- lm(y4_ventralattn ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss >= 114.50)) 
summary(topf_top_y4ventral)

topf_top_y5limbic <- lm(y5_limbic ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss >= 114.50)) 
summary(topf_top_y5limbic)

topf_top_y6frontoparietal <- lm(y6_frontoparietal ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss >= 114.50)) 
summary(topf_top_y6frontoparietal)

topf_top_y7defaultmode <- lm(y7_defaultmode ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss >= 114.50)) 
summary(topf_top_y7defaultmode)


```

```{r}

wtar_bottom_y1visual <- lm(y1_visual ~ wtar_efsiq, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq <= 104.0)) 
summary(wtar_bottom_y1visual)

wtar_bottom_y2somato <- lm(y2_somatomotor ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq <= 104.0))
summary(wtar_bottom_y2somato)

wtar_bottom_y3dorsalattn <- lm(y3_dorsalattn ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq <= 104.0))
summary(wtar_bottom_y3dorsalattn)

wtar_bottom_y4ventral <- lm(y4_ventralattn ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq <= 104.0))
summary(wtar_bottom_y4ventral)

wtar_bottom_y5limbic <- lm(y5_limbic ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq <= 104.0))
summary(wtar_bottom_y5limbic)

wtar_bottom_y6frontoparietal <- lm(y6_frontoparietal ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq <= 104.0))
summary(wtar_bottom_y6frontoparietal)

wtar_bottom_y7defaultmode <- lm(y7_defaultmode ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq <= 104.0))
summary(wtar_bottom_y7defaultmode)
```

```{r}
wtar_top_y1visual <- lm(y1_visual ~ wtar_efsiq, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq >= 118.0)) 
summary(wtar_top_y1visual)

wtar_top_y2somato <- lm(y2_somatomotor ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq >= 118.0))
summary(wtar_top_y2somato)

wtar_top_y3dorsalattn <- lm(y3_dorsalattn ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq >= 118.0))
summary(wtar_top_y3dorsalattn)

wtar_top_y4ventral  <- lm(y4_ventralattn ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq >= 118.0))
summary(wtar_top_y4ventral )

wtar_top_y5limbic <- lm(y5_limbic ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq >= 118.0))
summary(wtar_top_y5limbic)

wtar_top_y6frontoparietal <- lm(y6_frontoparietal ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq >= 118.0))
summary(wtar_top_y6frontoparietal)

wtar_top_y7defaultmode <- lm(y7_defaultmode ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq >= 118.0))
summary(wtar_top_y7defaultmode)
```

```{r}
topf_bottom_y1visual <- lm(y1_visual ~ topf_actual_ss, data=subset(df, diagonoses == "1" & topf_actual_ss <= 95.25)) 
summary(topf_bottom_y1visual)

topf_bottom_y2somato <- lm(y2_somatomotor ~ topf_actual_ss, data=subset(df,diagonoses == "1" & topf_actual_ss <= 95.25)) 
summary(topf_bottom_y2somato)

topf_bottom_y3dorsalattn <- lm(y3_dorsalattn ~ topf_actual_ss, data=subset(df,diagonoses == "1" & topf_actual_ss <= 95.25)) 
summary(topf_bottom_y3dorsalattn)

topf_bottom_y4ventral  <- lm(y4_ventralattn ~ topf_actual_ss, data=subset(df,diagonoses == "1" & topf_actual_ss <= 95.25)) 
summary(topf_bottom_y4ventral )

topf_bottom_y5limbic <- lm(y5_limbic ~ topf_actual_ss, data=subset(df,diagonoses == "1" & topf_actual_ss <= 95.25)) 
summary(topf_bottom_y5limbic)

topf_bottom_y6frontoparietal <- lm(y6_frontoparietal ~ topf_actual_ss, data=subset(df,diagonoses == "1" & topf_actual_ss <= 95.25)) 
summary(topf_bottom_y6frontoparietal)

topf_bottom_y7defaultmode <- lm(y7_defaultmode ~ topf_actual_ss, data=subset(df,diagonoses == "1" & topf_actual_ss <= 95.25))
summary(topf_bottom_y7defaultmode)
```


___plot
```{r}

graph0 =ggplot(total, aes(Age, FAS_total_raw))
 graph0 +
 geom_point(
        shape = 21,
        color = "#CBC3E3",
        fill = "#4B2E83",
        size = 4,
        stroke =1)  +
                xlim(0,100) +
                ylim(0,100) +
   theme(strip.background.x = element_rect(size = 0.5, linetype = "solid"),
         axis.line = element_line(colour = "#85754D", size = 2))+
   theme(
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.background = element_rect(fill = "#B7A57A",colour = NA),
         plot.background = element_rect(fill = "transparent",colour = NA)) +

             geom_smooth(method = 'lm', se =FALSE, color = "#4B2E83", size = 1.5)

```

---MCI: regression TOPF and LANG TESTS
---MCI: regression WTAR and LANG TESTS

```{r}
topf_fas_raw <- lm(fas_raw ~ topf_actual_ss, data=subset(df, diagonoses == "1"))
summary(topf_fas_raw)
####

topf_animal_raw <- lm(animal_raw~ topf_actual_ss, data=subset(df,diagonoses == "1"))
summary(topf_animal_raw)

topf_bnt <- lm(bnt_raw~ topf_actual_ss, data=subset(df,diagonoses == "1"))
summary(topf_bnt)

WTAR_fas_raw <- lm(fas_raw ~ wtar_efsiq, data=subset(df, diagonoses == "1"))
summary(WTAR_fas_raw)
####

WTAR_animal_raw <- lm(animal_raw~ wtar_efsiq, data=subset(df,diagonoses == "1"))
summary(WTAR_animal_raw)

WTAR_bnt <- lm(bnt_raw~ wtar_efsiq, data=subset(df,diagonoses == "1"))
summary(WTAR_bnt)
####
```
___Dementia,AD: regression TOPF and LANG TESTS
___Dementia,AD: regression WTAR and LANG TESTS

```{r}
topf_fas_raw_AD <- lm(fas_raw ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1"))
summary(topf_fas_raw_AD)

topf_animal_raw_AD <- lm(animal_raw~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1"))
summary(topf_animal_raw_AD)

topf_bnt_AD <- lm(bnt_raw~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1"))
summary(topf_bnt_AD)

WTAR_fas_raw_AD <- lm(fas_raw ~ wtar_efsiq, data=subset(df,diagonoses == "2" & df$etiology == "1"))
summary(WTAR_fas_raw_AD)
#######

WTAR_animal_raw_AD <- lm(animal_raw~ wtar_efsiq, data=subset(df,diagonoses == "2" & df$etiology == "1"))
summary(WTAR_animal_raw_AD)

WTAR_bnt_AD <- lm(bnt_raw~ wtar_efsiq, data=subset(df,diagonoses == "2" & df$etiology == "1"))
summary(WTAR_bnt_AD)

```



____Dementia, AD: top and bottom TOPF 

```{r}
###아무것도 없음
####TOP
topf_top_fas_raw_AD <- lm(fas_raw ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss >= 114.50)) 
summary(topf_top_fas_raw_AD)

topf_top_animal_raw_AD <- lm(animal_raw ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss >= 114.50))  
summary(topf_top_animal_raw_AD)

topf_top_bnt_raw_AD <- lm(bnt_raw ~ topf_actual_ss, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$topf_actual_ss >= 114.50)) 
summary(topf_top_bnt_raw_AD)

####BOTTOM
topf_bottom_fas_raw_AD  <- lm(fas_raw  ~ topf_actual_ss, data=subset(df, diagonoses == "2" & df$etiology == "1" & topf_actual_ss <= 95.25)) 
summary(topf_bottom_fas_raw_AD)

topf_bottom_animal_raw_AD <- lm(animal_raw ~ topf_actual_ss, data=subset(df, diagonoses == "2" & df$etiology == "1" & topf_actual_ss <= 95.25)) 
summary(topf_bottom_animal_raw_AD)

topf_bottom_bnt_raw_AD <- lm(bnt_raw ~ topf_actual_ss, data=subset(df, diagonoses == "2" & df$etiology == "1" & topf_actual_ss <= 95.25)) 
summary(topf_bottom_bnt_raw_AD)


```

___Dementia, AD: top and bottom WTAR 

```{r}
#########아무것도 없음
####TOP
wtar_top_fas_raw_AD <- lm(fas_raw ~ wtar_efsiq, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq >= 118.0)) 
summary(wtar_top_fas_raw_AD)

wtar_top_animal_raw_AD <- lm(animal_raw ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq >= 118.0))
summary(wtar_top_animal_raw_AD)

wtar_top_bnt_raw_AD <- lm(bnt_raw ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq >= 118.0))
summary(wtar_top_bnt_raw_AD )

####BOTTOM
wtar_bottom_fas_raw_AD <- lm(fas_raw ~ wtar_efsiq, data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq <= 104.0)) 
summary(wtar_bottom_fas_raw_AD)

wtar_bottom_animal_raw_AD <- lm(animal_raw ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq <=104.0))
summary(wtar_bottom_animal_raw_AD)

wtar_bottom_bnt_raw_AD  <- lm(bnt_raw ~ wtar_efsiq , data=subset(df,diagonoses == "2" & df$etiology == "1" & df$wtar_efsiq >= 104.0))
summary(wtar_bottom_bnt_raw_AD )



```


____MCI: top and bottom TOPF 


```{r}
###아무것도 없음 
topf_top_fas_raw_MCI <- lm(fas_raw ~ topf_actual_ss, data=subset(df,diagonoses == "1" & df$topf_actual_ss >= 114.50)) 
summary(topf_top_fas_raw_MCI)

topf_top_animal_raw_MCI <- lm(animal_raw ~ topf_actual_ss, data=subset(df,diagonoses == "1" & df$topf_actual_ss >= 114.50)) 
summary(topf_top_animal_raw_MCI)

topf_top_bnt_raw_MCI <- lm(bnt_raw ~ topf_actual_ss, data=subset(df,diagonoses == "1" & df$topf_actual_ss >= 114.50)) 
summary(topf_top_bnt_raw_MCI)

####BOTTOM
topf_bottom_fas_raw_MCI  <- lm(fas_raw  ~ topf_actual_ss, data=subset(df, diagonoses == "1" & topf_actual_ss <= 95.25)) 
summary(topf_bottom_fas_raw_MCI)

topf_bottom_animal_raw_MCI <- lm(animal_raw ~ topf_actual_ss, data=subset(df,diagonoses == "1" & topf_actual_ss <= 95.25)) 
summary(topf_bottom_animal_raw_MCI)

topf_bottom_bnt_raw_MCI <- lm(bnt_raw ~ topf_actual_ss, data=subset(df,diagonoses == "1" & topf_actual_ss <= 95.25)) 
summary(topf_bottom_bnt_raw_MCI)

```


____MCI: top and bottom WTAR
```{r}
wtar_top_fas_raw_MCI <- lm(fas_raw ~ wtar_efsiq, data=subset(df,diagonoses == "1" & df$wtar_efsiq >= 118.0)) 
summary(wtar_top_fas_raw_MCI)
#####

wtar_top_animal_raw_MCI <- lm(animal_raw ~ wtar_efsiq , data=subset(df,diagonoses == "1" & df$wtar_efsiq >= 118.0)) 
summary(wtar_top_animal_raw_MCI)

wtar_top_bnt_raw_MCI <- lm(bnt_raw ~ wtar_efsiq , data=subset(df,diagonoses == "1" & df$wtar_efsiq >= 118.0)) 
summary(wtar_top_bnt_raw_MCI )

####BOTTOM
wtar_bottom_fas_raw_MCI <- lm(fas_raw ~ wtar_efsiq, data=subset(df,diagonoses == "1"  & df$wtar_efsiq <= 104.0)) 
summary(wtar_bottom_fas_raw_MCI)
######

wtar_bottom_animal_raw_MCI <- lm(animal_raw ~ wtar_efsiq , data=subset(df,diagonoses == "1"  & df$wtar_efsiq <= 104.0)) 
summary(wtar_bottom_animal_raw_MCI)

wtar_bottom_bnt_raw_MCI  <- lm(bnt_raw ~ wtar_efsiq , data=subset(df,diagonoses == "1"  & df$wtar_efsiq <= 104.0)) 
summary(wtar_bottom_bnt_raw_MCI )
#####
```

___demographic

```{r}

kableone(CreateTableOne(total,vars = c('Age','ethnic','etiology'), strata = 'diag', test=FALSE))

```

___correlations

```{r}

yeo_7 <- total %>% select(contains('y7n'))
paper_pencils <- total[,23:32] %>% mutate_all(funs(as.numeric(as.character(.))))
combined_corr <- cor(bind_cols(yeo_7,paper_pencils), use = "pairwise.complete.obs")

```

___plot 1 all 4 diagnoses

```{r}

corrplot(combined_corr[0:7,8:17], method='number')


#a <- ggplot(total, aes(x = eFSIQ, y =  y7n1_visual_ct, color = diag)) +
#  geom_point() +
#  geom_smooth(method = "lm") +
#  facet_wrap(~diag) +
#   xlim(70, 140) + 
#   ylim(1.55,2.5)



#lm <- ggplot(total, aes(x =  eFSIQ , y = y7n1_visual_ct, color = diag)) + 
#                    geom_point() +   
#                    geom_smooth(method = "lm") + 
#                    facet_wrap(~diag)



#lm <- ggplot(total, aes(x =  eFSIQ , y = y7n1_visual_ct, color = diag)) + geom_point() + geom_smooth(method = "lm")
#+ facet_wrap(~total$diag)

#data <- ddply(total, .(sub_id, Accuracy), transform, RTOutlier = ifelse((RT > (mean(RT) + #3*sd(RT))) | (RT < (mean(RT) - 3*sd(RT))), 1, 0))
```


___Plot 2 : syndrome_v2_v2 1: MCI


```{r}
MCI <- subset(total, syndrome_v2_v2 == '1')

yeo_7_MCI <- MCI %>% select(contains('y7n')) 
paper_pencils_MCI <- MCI[,23:32] %>% mutate_all(funs(as.numeric(as.character(.))))
combined_corr_MCI <- cor(bind_cols(yeo_7_MCI, paper_pencils_MCI), use = "pairwise.complete.obs")



hello <- rcorr(as.matrix(combined_corr_MCI),type="pearson")        
         
corrplot(combined_corr_MCI[0:7,8:17], method='number')





```


___Plot 3 : syndrome_v2_v2 2: dementia

```{r pressure, echo=FALSE}
dementia <- subset(total, syndrome_v2_v2 == '2')

yeo_7_dementia <- dementia %>% select(contains('y7n')) 
paper_pencils_dementia <- dementia[,23:32] %>% mutate_all(funs(as.numeric(as.character(.))))
combined_corr_dementia <- cor(bind_cols(yeo_7_dementia,paper_pencils_dementia), 
                                       use = "pairwise.complete.obs")

corrplot(combined_corr_dementia[0:7,8:17],method='number')
```

___Plot 4 : syndrome_v2_v2 3: normal cognition

```{r}

HC <- subset(total, syndrome_v2_v2 == '3')

yeo_7_HC <- HC %>% select(contains('y7n')) 
paper_pencils_HC <- HC[,23:32] %>% mutate_all(funs(as.numeric(as.character(.))))
combined_corr_HC <- cor(bind_cols(yeo_7_HC,paper_pencils_HC), 
                                       use = "pairwise.complete.obs")

corrplot(combined_corr_HC[0:7,8:17],method='number')

```

